---
title: "LiveSessionAssignment-10"
author: "Rajni Goyal"
date: "November 8, 2016"
output:
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Unit 10 Live Session Prep Instructions:
#####•	Create a new variable ageGroup that categorizes age into following groups:< 18, 18–24, 25–34, 35–44, 45–54, 55–64 and 65+.
#####•	Use sub set of data called “ImpSub” where Impressions > 0 ) in your data set.
#####•	Create a new variable called click-through-rate (CTR = click/impression).
#####•	Use this ImpSub data set to do further analysis.
#####•	Plot distributions of number impressions and click-through-rate (CTR = click/impression) for the age groups.
#####•	Define a new variable to segment users based on click -through-rate (CTR) behavior-CTR< 0.2, 0.2<=CTR <0.4, 0.4<= CTR<0.6, 0.6<=CTR<0.8, CTR>0.8
#####•	Get the total number of Male, Impressions, Clicks and Signed_In (0=Female, 1=Male)
#####•	 Get the mean of Age, Impressions, Clicks, CTR and percentage of males and signed_In 
#####•	Get the means of Impressions, Clicks, CTR and percentage of males and signed_In  by AgeGroup.
#####•	Create a table of CTRGroup vs AgeGroup counts.
#####•	Plot distributions of number impressions and click-through-rate (CTR = click/impression) for the age groups
#####•	One more plot you think which is important to look at.

###Load libraries and data
```{r}
library(ggplot2)
library(doBy)
library(caroline)
```
### Data obtained in zipped form from GitHub at https://github.com/oreillymedia/doing_data_science
```{r}
data1 <- read.csv(url("http://stat.columbia.edu/~rachel/datasets/nyt5.csv"))
head(data1)
```
###Create age_group variable to categorize by ages < 18, 18-24, 25-34, 35-44, 45-54, 55-64 and 65+
```{r}
## Create age_group category
data1$ageGroup <-cut(data1$Age,c(-Inf,18,24,34,44,54,64,Inf))# Categorize users by "<18","18-24","25-34","35-44","45-54","55-64", and "65+"
head(data1)# Check to see that age_group categories added
levels(data1$ageGroup) <- c("<18","18-24","25-34","35-44","45-54","55-64","65+") # Update category names (cut() created factor so we need to change the factor levels)
levels(data1$ageGroup)  # Confirm change
head(data1)
```
###Plot Impressions by age_group for EDA
```{r}
## Explore Impressions by age_group
ggplot(data = data1, aes(x=ageGroup, y=Impressions, fill=ageGroup)) +
    geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=23, size=3, fill="blue") +     # Add blue mean diamond marker to boxplot
    xlab("Age Group") + ylab("Number of Impressions") + ggtitle("Number of Impressions by Age Group")
```
## Add CTR column
```{r}
impsub<-subset(data1, Impressions>0)
head(impsub)
impsub$CTR <- impsub$Clicks/impsub$Impressions
head(impsub)
y=t(impsub$Gender)
ncol(y)
y3=t(impsub$Signed_In)
ncol(y3)
#CTR = data1$click/impsub
```
###Plot CTR for EDA
```{r}
ggplot(data =impsub, aes(x=ageGroup, y=CTR, fill=ageGroup)) +
    geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=23, size=3, fill="blue") +     # Add blue mean diamond marker to boxplot
    xlab("Age Group") + ylab("CTR (Clicks/Impressions)") + ggtitle("Click-Through-Rate by Age Group")

```



###Plot log of CTR for EDA
```{r}
ggplot(data = impsub, aes(x=ageGroup, y=log(CTR), fill=ageGroup)) +
    geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=23, size=3, fill="blue") +     # Add blue mean diamond marker to boxplot
    xlab("Age Group") + ylab("Logarithmic CTR (Clicks/Impressions)") + ggtitle("Logarithmic Click-Through-Rate by Age Group") # Provide labels
```
### Define a new variable to segment users based on click -through-rate (CTR) behavior
```{r}
impsub$CTRSeg <-cut(impsub$CTR,c(-Inf,0.2,0.4,0.6,0.8,Inf))
head(impsub)
levels(impsub$CTRSeg) <- c("CTR<0.2","0.2<=CTR<0.4","0.4<=CTR<0.6","0.6<=CTR<0.8","CTR>0.8") 
levels(impsub$CTRSeg)
```
### Get the total number of Male, Impressions, Clicks and Signed_In
```{r}
head(impsub)
impsubMale<-subset(impsub, Gender>0)
head(impsubMale)
x=t(impsubMale$Gender)
ncol(x)
x1=t(impsubMale$Impressions)
ncol(x1)
x2=t(impsubMale$Clicks)
ncol(x2)
x3=t(impsubMale$Signed_In)
ncol(x3)
pctMale<-(ncol(x)/ncol(y))*100
pctMale
pctSigned<-(ncol(x3)/ncol(y3))*100
pctSigned
```
### Get the mean of Age, Impressions, Clicks, CTR and percentage of males and signed_In 
```{r}
sapply(impsubMale, mean, na.rm=TRUE)

```
### Get the means of Impressions, Clicks, CTR and percentage of males and signed_In  by AgeGroup.
```{r}
meanImp<-tapply(impsubMale$Impressions, impsubMale$ageGroup, mean, na.rm=TRUE) 
meanImp
meanclicks<-tapply(impsubMale$Clicks, impsubMale$ageGroup, mean, na.rm=TRUE) 
meanclicks
meanCTR<-tapply(impsubMale$CTR, impsubMale$ageGroup, mean, na.rm=TRUE) 
meanCTR
meanMale<-tapply(impsubMale$Gender, impsubMale$ageGroup, sum, na.rm=TRUE) 
meanMale
meanMalepct<-as.data.frame(meanMale)
meanMalepct1<-meanMalepct/ncol(x)*100
meanMalepct1
meanSigned<-tapply(impsubMale$Signed_In, impsubMale$ageGroup, sum, na.rm=TRUE) 
meanSigned
meanSignedpct<-as.data.frame(meanSigned)
meanSignedpct1<-meanSignedpct/ncol(x3)*100
meanSignedpct1
```
### Create a table of CTRGroup vs AgeGroup counts
```{r}

clen <- function(x){c(length(x))}
etable1<-summaryBy(CTRSeg~ageGroup,data = impsubMale, FUN=clen)
etable1
etable2<-summaryBy(ageGroup~CTRSeg,data = impsubMale, FUN=clen)
etable2
```
###Plot Impressions by age_group for EDA
```{r}

ggplot(data = impsubMale, aes(x=ageGroup, y=Impressions, fill=ageGroup)) +
    geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=23, size=3, fill="blue") +     # Add blue mean diamond marker to boxplot
    xlab("Age Group") + ylab("Number of Impressions") + ggtitle("Number of Impressions by Age Group")
```
###Plot CTR for EDA
```{r}
ggplot(data =impsubMale, aes(x=ageGroup, y=CTR, fill=ageGroup)) +
    geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=23, size=3, fill="blue") +     # Add blue mean diamond marker to boxplot
    xlab("Age Group") + ylab("CTR (Clicks/Impressions)") + ggtitle("Click-Through-Rate by Age Group")
```


###Plot log of CTR for EDA
```{r}
ggplot(data = impsubMale, aes(x=ageGroup, y=log(CTR), fill=ageGroup)) +
    geom_boxplot() + stat_summary(fun.y=mean, geom="point", shape=23, size=3, fill="blue") +     # Add blue mean diamond marker to boxplot
    xlab("Age Group") + ylab("Logarithmic CTR (Clicks/Impressions)") + ggtitle("Logarithmic Click-Through-Rate by Age Group") # Provide labels

```